Recognizing emotions with technology and starting discussions

### 2018-01-21 paper.tex
Add method, start on results

\section{Method}
To be added

@@

\section{Results}
To be added

@@

>>>>

\section{Method} \label{method}
After thoroughly testing the prototype on every aspect, working towards answering the main question was imminent.
\emph{Does the visualization of emotions of young people (aged 16-26) by facial expression
recognition software, lead to discussion regarding the displayed content?}

The research that we performed was qualitative research. Our prototype was built for testing purposes, and not
as an end-product. Therefore, we greatly value any feedback and improvement suggestions for our prototype from
our research participants, as this can be used in future development. Because we are researching
different emotional reactions of users, we're looking for very specific results. This means that our research
design is very specific as well. The research design has the following requirements:
\begin{itemize}
    \item{Users of the prototype have to be in a closed-off room to prevent any distractions which can affect
    test results.}
    \item{Users of the prototype will not be given any information regarding the purpose or operation of the
    prototype, since this can affect their emotional reactions and therefore the test results.}
    \item{Users will be asked to use the prototype one-by-one.}
    \item{Users of the prototype will be asked a set of questions which will be focused on accuracy
    and improvement of the prototype.}
    \item{Each video shown by the prototype has a maximum length of one minute due to technical restrictions.}
\end{itemize}

\subsection{Participants}
The participants are aged between 16-26 years old, and were scouted at the Amsterdam University of Applied
Sciences. The participants were invited into a reserved, closed-off classroom, located at the Wibautstraat, where
they were able to test the prototype. Our goal was to invite at least 20 participants. Unfortunately, due to
technical difficulties and time restrictions, we've only managed to get 13 participants.

\subsection{Content}
The video had to provoke a measurable reaction from the subjects. Therefore, it is important that we show content
that is doing just that. Research conducted by the Journal of Social Psychology \cite{leary2015seemingly}
has shown that the strongest emotional reaction by people is caused by showing pictures of traumatic events.
However, we wanted our subjects to show multiple emotions, and not just the ones that are associated with
traumatic events, like \emph{fear} and \emph{disgust}. Therefore, we decided to show the subjects content
that is, in any way, provoking. We have selected three videos which have been edited to last roughly one minute:
\begin{enumerate}
    \item{Roast of Giel Beelen (Peter Pannekoek roast)}
    \item{Asian longnecks: Why does this culture consider this beauty?}
    \item{Failarmy, best fails of 2017}
\end{enumerate}

@@

\section{Results}
As described in \ref{method}, we have conducted prototype testing sessions with 13 participants. For each of these
participants, we have two pieces of data:
\begin{itemize}
    \item{Predicted emotions during the shown video, created by the prototype}
    \item{Results from the interview we had with each participant during the testing}
\end{itemize}
Furthermore, for every of the three available videos, we have expectations regarding the emotions at certain
times of the video. Using these pieces of data, we are interested in the following information from analyzing
the results:
\begin{itemize}
    \item{Do the participants agree with the emotions predicted by the prototype?}
    \item{Do the predicted emotions coincide with the expectations we had from certain videos?}
\end{itemize}

@@

\section{Conclusion}
To be added
